%-------------------------
% Resume in Latex
% Author : Rohan Batra
% Variant: SoftwareEngineering
%------------------------


\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} 
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% ----------- MARGIN TUNING FOR 1 PAGE -----------
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\textwidth}{1.15in}
\addtolength{\topmargin}{-0.65in}
\addtolength{\textheight}{1.35in}

\raggedright
\setlength{\tabcolsep}{0pt}
\setlength{\parskip}{0pt}

% ----------- SECTION SPACING -----------
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{#1}
}

\newcommand{\resumeSubheading}[4]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.12in, label={}, topsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[noitemsep, topsep=0pt, leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\vspace{-12pt}
\begin{center}
    \textbf{\Huge \scshape Rohan Batra} \\ \vspace{1pt}
    \small 
    \href{tel:+917417879921}{+91-74178-79921} $|$ 
    \href{mailto:contact@rohanbatra.in}{contact@rohanbatra.in} $|$
    \href{https://linkedin.com/in/rohanbatrain}{linkedin.com/in/rohanbatrain} $|$
    \href{https://github.com/rohanbatrain}{github.com/rohanbatrain} $|$
    \href{https://rohanbatra.in}{rohanbatra.in}
\end{center}
\vspace{-10pt}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {UPES Dehradun}{Dehradun, India}
    {B.Tech. in Computer Science and Engineering}{Expected Aug 2027}
  \resumeItemListStart
    \resumeItem{Cumulative GPA: 7.97 $|$ Coursework: Data Structures, OOPS with C++, DBMS, OS}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Software Engineer Intern}{Nov 2025 -- Present}
    {Techymonks}{Bangalore, India (Remote)}
  \resumeItemListStart
    \resumeItem{Developing secure full-stack modules using \textbf{Agile/SDLC} practices.}
    \resumeItem{Applying \textbf{OWASP Top 10} security controls for sensitive data protection.}
    \resumeItem{Building \textbf{WCAG 2.0}-compliant accessible and responsive UI components.}
    \resumeItem{Collaborating cross-functionally with design and backend teams.}
  \resumeItemListEnd

  \resumeSubheading
    {Technical Head}{Sep 2025 -- Present}
    {\href{https://www.linkedin.com/company/gdsc-upes/}{Google Developer Groups On Campus (GDGOC) UPES}}{Dehradun, India}
  \resumeItemListStart
    \resumeItem{Delivered \href{https://www.linkedin.com/posts/rohanbatrain_cloudnative-gdg-engineering-activity-7400975128945283072-RaC4}{\underline{large-scale technical workshops}} to 100+ attendees.}
    \resumeItem{Led cross-functional teams delivering production-grade workshops and technical initiatives.}
    \resumeItem{Mentored juniors in cloud, web, and system design fundamentals.}
  \resumeItemListEnd

  \resumeSubheading
    {Co-Founder}{Sep 2023 -- Apr 2025}
    {\href{https://linuxwale.in}{LinuxWale}}{Dehradun, India}
  \resumeItemListStart
    \resumeItem{Guided 10+ users through Linux migration and system optimization.}
    \resumeItem{Managed community-driven technical projects independently.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\href{https://github.com/rohanbatrain/Karmstrot-Builds}{\textbf{Karmstrot Builds (Android \& C++)}} $|$ \emph{C++, Shell, Android SDK}}{Aug 2024 -- Present}
  \resumeItemListStart
    \resumeItem{Built automated integration scripts for Android KernelSU using Shell and C++.}
    \resumeItem{Modified system-level configurations using the Android SDK across devices.}
    \resumeItem{Applied structured SDLC practices for versioning and QA validation.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\href{https://github.com/rohanbatrain/second_brain_database}{\textbf{Second Brain Database}} $|$ \emph{Python, FastAPI, Redis, OAuth, RBAC}}{Nov 2024 -- Present}
  \resumeItemListStart
    \resumeItem{Developed secure APIs using OAuth2 and RBAC for sensitive data protection.}
    \resumeItem{Designed optimized relational schemas for fast data retrieval.}
    \resumeItem{Containerized services with Docker enabling CI/CD stability.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\href{https://github.com/rohanbatrain/n8n-nodes-second-brain-database}{\textbf{n8n Nodes – Second Brain Database}} $|$ \emph{n8n, JavaScript, Automation}}{Jan 2025 -- Present}
  \resumeItemListStart
    \resumeItem{Built custom n8n nodes to integrate workflows directly with the Second Brain Database.}
    \resumeItem{Enabled end-to-end automation pipelines using JavaScript-based workflow orchestration.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\href{https://github.com/rohanbatrain/MarkLang}{\textbf{MarkLang}} $|$ \emph{Programming Language, Tooling}}{Jan 2025 -- Present}
  \resumeItemListStart
    \resumeItem{Designed and implemented a custom programming language and compiler toolchain.}
    \resumeItem{Worked on syntax design, parsing, and execution pipeline.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\href{https://github.com/rohanbatrain/proxmox-auto-install-assistant-docker}{\textbf{Proxmox Auto-Install Assistant}} $|$ \emph{Automation, Infrastructure}}{Jan 2025 -- Present}
  \resumeItemListStart
    \resumeItem{Automated Linux installer reducing manual configuration time by 80\%.}
    \resumeItem{Improved usability of complex system partitioning workflows.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\href{https://github.com/rohanbatrain/Portfolio}{\textbf{Portfolio \& Resume CI/CD Automation}} $|$ \emph{CI/CD, GitHub Actions, LaTeX}}{Jan 2025 -- Present}
  \resumeItemListStart
    \resumeItem{Built a CI/CD pipeline that auto-generates and deploys this résumé from LaTeX on every commit.}
    \resumeItem{Maintains a fully version-controlled, production-ready developer portfolio.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}, topsep=0pt]
\small{\item{
 \textbf{Languages}{: C/C++, Python, JavaScript, HTML, CSS, SQL, Bash} \\
 \textbf{Web \& Mobile}{: Responsive Design, Android SDK, REST APIs, OOD} \\
 \textbf{Systems}{: Linux, Docker, CI/CD, GitHub Actions} \\
 \textbf{Security \& Accessibility}{: OAuth2, RBAC, OWASP, WCAG 2.0} \\
 \textbf{Productivity}{: MS Excel, Word, PowerPoint, VS Code, Git}
}}
\end{itemize}

\end{document}
