\documentclass[a4paper,10pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{parskip}
\usepackage{fontawesome}

% Hyperlink setup 
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
}

% Header formatting
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\thepage}

% Title Formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[.]

% Begin Document
\begin{document}

% Header
\begin{center}
    {\Huge \textbf{Rohan Batra}} \\[6pt]
    Vikasnagar, Uttarakhand, India \\
    \small \faEnvelope \hspace{0.1cm} \href{mailto:contact@rohanbatra.in}{contact@rohanbatra.in} \quad 
    \faPhone \hspace{0.1cm} 7253069231 \quad 
    \faLinkedinSquare \hspace{0.1cm} \href{https://linkedin.com/in/rohanbatrain}{linkedin.com/in/rohanbatrain} \quad 
    \faGlobe \hspace{0.1cm} \href{https://rohanbatra.in}{rohanbatra.in} \\
\end{center}

\vspace{10pt} % Spacing

% Summary Section
\section*{Summary}
\noindent
Motivated software developer with experience in WordPress, Python applications, and Unreal Engine rendering. Passionate about open-source contributions, exemplified through the \textit{Second-Brain-Tools} project. Skilled in Python libraries and problem-solving with a commitment to delivering high-quality work.

% Experience Section
\section*{Experience}

\subsection*{Co-Founder, Kruxers (Web Development)}
\begin{itemize}[left=0em, itemsep=3pt]
    \item Led strategic planning, establishing Kruxers as a scalable web development and hosting solutions provider.
    \item Directed startup ideation, targeting web hosting solutions for client scalability.
\end{itemize}

\subsection*{Website Developer, Kruxers}
\begin{itemize}[left=0em, itemsep=3pt]
    \item Utilized Git for version control and contributed to CMS development, optimizing website performance.
    \item Enhanced website user experience by reducing load times and improving content accessibility.
\end{itemize}

\subsection*{Tech Lead, Kruxers Gaming}
\begin{itemize}[left=0em, itemsep=3pt]
    \item Joined an esports venture, applying prior experience to improve branding and operational strategies.
\end{itemize}

\subsection*{Founder \& CEO, Ravage}
\begin{itemize}[left=0em, itemsep=3pt]
    \item Led a small esports team, organizing tournaments and developing a content strategy for YouTube.
\end{itemize}

% Internship Section
\section*{Internship}

\subsection*{Intern, Uttarakhand Blind Sports Association (UBSA)}
\textit{Uttarakhand, India} \hfill \textit{June 2023 – July 2023} \\
\begin{itemize}[left=0em, itemsep=3pt]
    \item Collaborated closely with visually impaired athletes, enhancing empathy and understanding of inclusivity.
    \item Developed a commitment to accessibility and social justice advocacy, supporting the rights of disabled individuals.
    \item Inspired to leverage skills for awareness campaigns and educational initiatives promoting inclusivity.
\end{itemize}

% Projects Section
\section*{Projects}

\subsection*{Development Setup (Personal Project) | April 2023 - Present}
\begin{itemize}[left=0em, itemsep=3pt]
    \item Customized Android setups, including ROMs and Magisk; configured Proxmox and Arch Linux systems.
    \item Managed code using Termux for seamless collaboration directly from Android.
\end{itemize}

\subsection*{Second-Brain-Tools-2022 (Open Source) | Nov 2022 - Dec 2022}
\begin{itemize}[left=0em, itemsep=3pt]
    \item Created a Second Brain toolkit featuring a bookmark manager, personal wiki, and note-taking tools.
\end{itemize}

\subsection*{LMCottage (Web Development) | Sept 2022 - Oct 2022}
\begin{itemize}[left=0em, itemsep=3pt]
    \item Developed a WordPress website, optimizing for performance and troubleshooting.
\end{itemize}

\subsection*{Pahari Village Resort (3D Render) | Oct 2020 - Dec 2020}
\begin{itemize}[left=0em, itemsep=3pt]
    \item Produced immersive 3D renders using Unreal Engine, translating client vision into realistic environments.
\end{itemize}

% Education Section
\section*{Education}
\noindent
\textbf{Senior Secondary Education} \\
St. Mary's Convent Sr. Sec. School, Vikasnagar, Dehradun \\
2023

\noindent
\textbf{Matriculation} \\
St. Mary's Convent Sr. Sec. School, Vikasnagar, Dehradun \\
2021

% Certifications Section
\section*{Certifications}
\begin{itemize}[left=0em, itemsep=3pt]
    \item \textbf{Eureka Junior Semifinalist} - Ecell IIT Bombay | 2022, 2021 \\
    Semifinalist in entrepreneurial competition, showcasing business acumen and collaboration.
    \item \textbf{English Essay Writing} - St. Mary's Convent Sr. Sec. School | 2022 \\
    Achieved first place in English essay competition.
\end{itemize}

% Skills Section
\section*{Skills}
\begin{itemize}[left=0em, itemsep=3pt]
    \item \textbf{System Setup \& Administration:} Proxmox, Arch Linux, Termux
    \item \textbf{Android Customization:} Custom ROMs, Magisk, Bootloader unlocking
    \item \textbf{3D Rendering:} Unreal Engine, textures, camera work
    \item \textbf{Programming:} Python, terminal applications
    \item \textbf{Web Development:} WordPress, Git
\end{itemize}

\end{document}
