%-------------------------
% Resume in Latex
% Author : Rohan Batra
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Rohan Batra} \\ \vspace{1pt}
    \small 741-787-9921 $|$ \href{mailto:contact@rohanbatra.in}{\underline{contact@rohanbatra.in}} $|$
    \href{https://linkedin.com/in/rohanbatrain}{\underline{linkedin.com/in/rohanbatrain}} $|$
    \href{https://github.com/rohanbatrain}{\underline{github.com/rohanbatrain}} $|$
    \href{https://rohanbatra.in}{\underline{rohanbatra.in}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {UPES Dehradun}{Dehradun, India}
      {B.Tech. in Computer Science and Engineering}{Expected Aug 2027}
      \resumeItemListStart
        \resumeItem{Cumulative GPA: 7.97}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer Intern}{Nov 2025 -- Present}
      {Techymonks}{Bangalore, India (Remote)}
      \resumeItemListStart
        \resumeItem{Focusing on full-stack development with exposure to secure software lifecycle and CI/CD best practices.}
        \resumeItem{Working directly with the Director to build resilient, scalable systems applying security-by-design principles.}
        \resumeItem{Collaborating within an Agile team to deliver production-ready components with automated workflows.}
      \resumeItemListEnd

    \resumeSubheading
      {Technical Head}{Sep 2025 -- Present}
      {Google Developer Groups On Campus (GDGOC) UPES}{Dehradun, India}
      \resumeItemListStart
        \resumeItem{Leading and mentoring 5 technical leads and contributor teams, ensuring high-quality engineering outcomes.}
        \resumeItem{Managing technical execution of large events with cross-functional coordination and infrastructure reliability.}
        \resumeItem{Driving upskilling initiatives focused on cloud, automation, and modern development workflows.}
      \resumeItemListEnd

    \resumeSubheading
      {Co-Founder}{Sep 2023 -- Apr 2025}
      {LinuxWale}{Dehradun, India}
      \resumeItemListStart
        \resumeItem{Initiative focused on teaching Linux fundamentals, digital freedom, and FOSS adoption.}
        \resumeItem{Assisted 5–10 individuals in migrating from Windows to Linux, learning terminal basics, system architecture, and choosing their own operating system.}
        \resumeItem{Co-founded the community with \href{https://harshdeepsingh.in}{\underline{Harshdeep Singh}} before transitioning to full-time work on the Second Brain Database.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
          {\textbf{Second Brain Database} $|$ \emph{Python, FastAPI, MongoDB, Redis, Docker, LangChain}}{Nov 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Designed a secure, scalable KBMS using \textbf{FastAPI} and \textbf{Motor} with asynchronous backend architecture.}
            \resumeItem{Integrated AI agents via \textbf{LangChain/LangGraph} and \textbf{Ollama} with real-time processing using \textbf{LiveKit} and \textbf{Deepgram}.}
            \resumeItem{Implemented \textbf{JWT/OAuth/MFA}, rate limiting, and secure API design with RBAC-based workspace control.}
            \resumeItem{Set up a DevSecOps pipeline using \textbf{GitHub Actions, Prometheus, Loki}, and automated vulnerability scanning.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{IPAM (powered by Second Brain Database)}}{Sep 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a hierarchical IP Address Management for 10.X.Y.Z IPv4 spaces with automated allocation logic.}
            \resumeItem{Engineered multi-tenant isolation with \textbf{RBAC}, secure namespaces, and infrastructure-hardening practices.}
            \resumeItem{Built automated reservation and monitoring workflows with webhook notifications and expiry logic.}
            \resumeItem{Implemented audit trails, utilization analytics, and anomaly indicators to prevent misconfiguration.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Bash/Shell, HTML, YAML, SQL, MongoDB} \\
     \textbf{Frameworks}{: FastAPI, Celery, LangChain, LangGraph, FastMCP, Uvicorn} \\
     \textbf{Developer Tools}{: Git, Docker, GitHub Actions, Make, Prometheus, Loki, Bandit, pytest, security scanners} \\
     \textbf{Security \& DevSecOps}{: JWT/OAuth/MFA, API security, RBAC, CI/CD security integration, SIEM basics, vulnerability assessment} \\
     \textbf{Libraries \& APIs}{: Motor, Redis, Pydantic, Cryptography, Deepgram, LiveKit, FFmpeg, Qdrant, Ollama}
    }}}
 \end{itemize}

%-------------------------------------------
\end{document}


Cybersecurity resume 